### 2010-10-07 Thesis/Appendix1.tex
Delete most of dummy contents
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@123 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
- Update 8 September -
Started writing of state of the art for shells + bib updated



git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@170 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
- Update 7 October -
Changes added in intro and conclusion + references improved + TODO removed



git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@183 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\chapter{Appendix Example}
\label{chap:appendix1}

\section{Appendix example section}

And I cite myself to show by bibtex style file (two authors) \citep{Commowick_MICCAI_2007}.

This for other bibtex stye file : only one author \cite{Oakes_RStat_1999} and many authors \cite{Guimond_CVIU_2000}.

>>>>

\chapter{The weighted residual method}
\label{appendix1}

The \emph{method of weighted residuals} is an approximation technique for solving differential equations. A subclass of this method, the \emph{Galerkin method of weighted residuals}, is often used to derive the element equations for the finite element method.

Let us suppose that we have a linear differential operator $ D $ acting on a function $ u $ to produce a function $ p $:
\begin{equation}
D(u(x)) = p(x).
\end{equation}
We wish to approximate $ u $ by a function $ \tilde{u} $, which is a linear combination of basis functions chosen from a linearly independent set, that is: 
\begin{equation}
u \approx \tilde{u} = \sum_{i=1}^n a_i \phi_i .
\end{equation}
Now, when substituted into the differential operator $ D $, the result of the operation is not, in general, $ p(x) $. Hence, an error or \emph{residual} will exist:
\begin{equation}
R(x) = D(\tilde{u}(x)-p(x)) \neq 0.
\end{equation}
The idea behind the weighted residual method is to force the residual to zero in some average sense over the domain:
\begin{equation}
\int_X R(x) W_i(x) dx = 0, \quad i = 1, 2, \ldots, n
\end{equation}
where the number of \emph{weight functions} $ W_i $ is exactly equal to the number of unknown constants $ a_i $ in $ \tilde{u} $. The result is a set of $ n $ algebraic equations for the unknown constants $ a_i $. Depending on the choice for $ W_i $, several sub-methods can be derived: collocation, sub-domain, least squares, Ritz, Galerkin etc.

%For instance, the weight function used by the Galerkin method \TODO{need to check this: Wi are the shape functions?} is:
%\begin{equation}
%W_i = \pd{\tilde{u}}{a_i}.
%\end{equation}

### 2010-10-07 Thesis/Chapter1.tex
- Update 7 October -
Changes added in intro and conclusion + references improved + TODO removed



git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@183 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

Virtually everyone knows this situation where a close relative has to go to the hospital, either for a simple routine check or a serious surgery. Hospitals are meant to be reinsuring, a refuge where people's health improves, where people get fixed. Obviously, patient safety is a critical concern in the medical industry. Yet, patients have been known to suffer injuries or even death due to errors of judgement or a lack of care and training. As an example, a report published in 2000 by the Institute of Medicine in the United States \citep{Kohn00} described two studies carried out in the 1990s based on large samples of hospital admissions. They found that the proportion of hospital admissions experiencing an adverse event, defined as causes of injuries by medical management, were 2.9 and $3.7\,$\%, respectively . The proportion of these events attributable to errors (that is, preventable adverse events, in other words medical errors) was 58 and $53\,$\%, respectively. Even when using the lower estimate, deaths due to preventable adverse events in 1997 in the US ($44\,000$) exceeded the deaths attributable to motor vehicle accidents ($43\,458$), breast cancer ($42\,297$) or AIDS ($16\,516$). Because many errors go unreported, detailed statistics on medical errors are fairly scarce (hospitals usually do not attempt to emphasize errors). Nevertheless, the problem is real. And this is not surprising, elaborate skills have to be mastered in the medical field. Moreover, achieving a high degree of personal competence is sometimes not sufficient as various members of staff must learn how to work as a team. In fact, one of the recommendations of this report \citep{Kohn00} was to \emph{establish interdisciplinary team training programs for providers that incorporate proven methods of training, such as simulation}. However, dispensing an appropriate training in such a complex and hazardous environment is very challenging. Because healthcare is a high risk industry (like aviation or military), training in the real world is too costly and dangerous. Consequently, various approaches were applied to teaching and training of medical practicians over history of healthcare.

@@

The most basic form of medical simulators are simple models of human anatomy. Hundreds of years ago, representations in clay and stone were already used to demonstrate clinical features of disease states and their effects on humans. Models have been found from many cultures and continents. Nowadays, similar passive models are still used to help students learn the anatomy. In medical schools, live animals are used for teaching physiology and surgery classes. Dogs, pigs, goats and sheep are commonly used in medical training. The exercices essentially consist in anesthetising the animal and practicing surgical techniques. They may also be severely injured to teach participants how to treat and manage various traumatic injuries. If animal training allows a better realism than passive models, this type of training is being progressively abandoned because of both the prohibitive cost and obvious ethical reasons. Alternatives include active models of human patients that attempt to reproduce living anatomy or physiology. The first example was created in the early 1960s by Asmund Laerdal for training in mouth to mouth ventilation. This simulator of a dying victim not breathing and lacking a heart beat, became known as called Resusci-Anne and had been widely used for CPR training thanks to an internal spring attached to the chest wall \citep{Cooper04}. In the mid-1960s, Sim One became the first mannequin controlled by a computer. The chest was moved with breathing, the eyes blinked and the pupils could dilate for instance. But the computer technology was too expensive for commercialisation at the time and only one mannequin was built. Over time, computerised mannequins have substantially improved and today such systems are essentially integrated into training centers that aim at recreating the operating room environment. Scenarios can be created to expose medical professionals to diverse clinical situations with the goal of improving the communication between staff members. Rare but critical clinical situations that may require specialised training can also be simulated. Another approach to medical training, that may also be combined with computerised mannequins, is the use of computer-based simulators. Such systems provide an elegant solution for medical training since they can offer a realistic and configurable training environment. Computer-based simulators also appear as an ideal tool for skill assessment of students since virtually every parameter of the simulation can be measured and recorded. Increasing computational power and growing interest for the field over the last decade led to the rapid development of reasonably sophisticated simulation systems. Yet, computer-based simulators still face numerous challenges.

@@

Because everything is virtual, the possibilities are almost infinite. Ultimately, the ideal simulator will feature a patient-specific anatomy obtained through a medical imaging technique (such as MRI or CT). It will also need to consider the actual properties of the anatomical structures of this given patient, to take into account both the variability across patients and the alteration due to possible diseases. Indeed, diseased organs are often much stiffer than healthy structures and this will affect the overall mechanical behaviour. The physiology relevant to the simulated procedure (motion caused by breathing, heart beat, blood flow, etc.) will have to be faithfully reproduced as well. Such a patient-specific simulator capable of replicating human physiology and pathologies would be a great instrument for medical training. Not only it would constitute an invaluable tool for teaching to medical students but it would also enable experts clinicians to practice rare and complex cases that they would otherwise never encounter before facing them. Moreover, a highly realistic simulator would also allow planning of complex surgical procedures and per-operative guidance.

While substantial progress was accomplished during the past ten years, much remains to be done. In fact, the research described in this PhD fits in the context of computed-based simulation. Medical simulation can be broken up into different areas of research, all are very challenging.
%
\begin{description}
\item[Photorealistic rendering:] first, the scene needs to look real. A rendered image can be understood in terms of a number of visible features that a simulated image wants to reproduce: colors, brightness, shadows, reflection, transparency, refraction, diffraction, etc. Therefore, a series of fairly complex calculations is required for all visible structures within each image (usually displayed at $30\,$Hz). 
\item[Collision detection] involves algorithms to check for collision between solids. Without them, tools could go through organs and other obstacles during the simulation. The collision detection algorithm has to find all intersections between the objects at each time step of the simulation. 
\item[Contact modelling:] once the collision between two objects has been detected, a variety of responses to this contact may be formulated. The two solids may rebound away from each other, slide (with or without friction), or settle into relative static contact. This step must also be carried out at each time step. 
\item[Anatomical structure modelling and haptic feedback:] the simulator must also take into account the physics involved in the deformation of anatomical structures. Indeed, when a pressure is exerted on a given organ, the latter must deform and react according to its mechanical properties. The force created by this interaction may be sent back to the user through a haptic device. This device provides the user with a sense of touch so he can feel the forces and vibrations due to the contact. The force feedback must take place at a very high frequency (often between $ 500 $ and $ 1\,000\,$Hz) for a smooth sense of touch. 
\end{description}
%
Although each of these steps alone is computationally demanding, the whole simulation process must be computed in real-time or close to real-time. Real-time means that one second of simulation corresponds to one second of real life. Of particular interest to us in this PhD is the accurate modelling of the deformation of anatomical structures in real-time.

>>>>

Virtually everyone knows this situation where a close relative has to go to the hospital, either for a simple routine check or a serious surgery. Hospitals are meant to be reinsuring, a refuge where people's health improves, where people get fixed. Obviously, patient safety is a critical concern in the medical industry. Yet, patients have been known to suffer injuries or even death due to errors of judgement or a lack of care and training. As an example, a report published in 2000 by the Institute of Medicine in the United States \citep{Kohn00} described two studies carried out in the 1990s based on large samples of hospital admissions. They found that the proportion of hospital admissions experiencing an adverse event, defined as causes of injuries by medical management, were 2.9 and $3.7\,$\%, respectively. The proportion of these events attributable to errors (that is, preventable adverse events, in other words medical errors) was 58 and $53\,$\%, respectively. Even when using the lower estimate, deaths due to preventable adverse events in 1997 in the US ($44\,000$) exceeded the deaths attributable to motor vehicle accidents ($43\,458$), breast cancer ($42\,297$) or AIDS ($16\,516$). Because many errors go unreported, detailed statistics on medical errors are fairly scarce (hospitals usually do not attempt to emphasize errors). Nevertheless, the problem is real. And this is not surprising, elaborate skills have to be mastered in the medical field. Moreover, achieving a high degree of personal competence is sometimes not sufficient as various members of staff must learn how to work as a team. In fact, one of the recommendations of this report \citep{Kohn00} was to \emph{establish interdisciplinary team training programs for providers that incorporate proven methods of training, such as simulation}. However, dispensing an appropriate training in such a complex and hazardous environment is very challenging. Because healthcare is a high risk industry (like aviation or military), training in the real world is too costly and dangerous. Consequently, various approaches were applied for teaching and training of medical practicians over history of healthcare.

@@

The most basic form of medical simulators are simple models of human anatomy. Hundreds of years ago, representations in clay and stone were already used to demonstrate clinical features of disease states and their effects on humans. Models have been found from many cultures and continents. Nowadays, similar passive models are still used to help students learn the anatomy. In medical schools, live animals are also used for teaching physiology and surgery classes. Dogs, pigs, goats and sheep are commonly used in medical training. The exercices essentially consist in anesthetising the animal and practicing surgical techniques. They may also be severely injured to teach participants how to treat and manage various traumatic injuries. If animal training allows a better realism than passive models, this type of training is being progressively abandoned because of both the prohibitive cost and obvious ethical reasons. Alternatives include active models of human patients that attempt to reproduce living anatomy or physiology. The first example was created in the early 1960s by Asmund Laerdal for training in mouth to mouth ventilation. This simulator of a dying victim not breathing and lacking a heart beat, became known as called Resusci-Anne and had been widely used for CPR training thanks to an internal spring attached to the chest wall \citep{Cooper04}. In the mid-1960s, Sim One became the first mannequin controlled by a computer. The chest was moved with breathing, the eyes blinked and the pupils could dilate for instance. But the computer technology was too expensive for commercialisation at the time and only one mannequin was built. Over time, computerised mannequins have substantially improved and today such systems are essentially integrated into training centers that aim at recreating the operating room environment. Scenarios can be created to expose medical professionals to diverse clinical situations with the goal of improving the communication between staff members. Rare but critical clinical situations that may require specialised training can also be simulated. Another approach to medical training, that may also be combined with computerised mannequins, is the use of computer-based simulators. Such systems provide an elegant solution for medical training since they can offer a realistic and configurable training environment. Computer-based simulators appear as an ideal tool to assess students' skills since virtually every parameter of the simulation can be measured and recorded. Increasing computational power and growing interest for the field over the last decade led to the rapid development of reasonably sophisticated simulation systems. Yet, computer-based simulators still face numerous challenges.

@@

Because computer-based simulators are entirely virtual, the possibilities are almost infinite. The ideal simulator will ultimately feature a patient-specific anatomy obtained through a medical imaging technique (such as MRI or CT). It will also consider the actual properties of the anatomical structures of this given patient, to take into account both the variability in mechanical properties across patients and potential alterations due to diseases. Indeed, diseased organs are often much stiffer than healthy structures and this will affect the overall mechanical behaviour. The physiology relevant to the simulated procedure (motion caused by breathing, heart beat, blood flow, etc.) will have to be faithfully reproduced as well. Such a patient-specific simulator capable of replicating human physiology and pathologies would be a great instrument for medical training. Not only it would constitute an invaluable tool for teaching to medical students but it would also enable experts clinicians to practice rare and complex cases that they would otherwise never encounter before facing them in real life. Moreover, a highly realistic simulator would also allow planning of complex surgical procedures and per-operative guidance.

While substantial progress was accomplished during the past ten years, much remains to be done. In fact, the research described in this PhD fits in this context of computed-based simulation. Medical simulation can be broken up into different areas of research, all are very challenging.
%
\begin{description}
\item[Photorealistic rendering:] first, the scene needs to look real. A rendered image can be understood in terms of a number of visible features that we want to reproduce in a simulated image: colors, brightness, shadows, reflection, transparency, refraction, diffraction, etc. Therefore, a series of fairly complex calculations is required for all visible structures within each image (usually displayed at $30\,$Hz). 
\item[Collision detection] involves algorithms to check for collision between solids. Without them, tools could go through organs and other obstacles during the simulation. The collision detection algorithm has to find all intersections between the objects at each time step of the simulation. 
\item[Contact modelling:] once the collision between two objects has been detected, a variety of responses to this contact may be formulated. The two solids may rebound away from each other, slide (with or without friction), or settle into relative static contact. This step must also be carried out at each time step. 
\item[Anatomical structure modelling and haptic feedback:] the simulator must also take into account the physics involved in the deformation of anatomical structures. Indeed, when a pressure is exerted on a given organ, the latter must deform and react according to its mechanical properties. The force created by this interaction may be sent back to the user through a so-called haptic device. This device provides the user with a sense of touch so he can feel the forces and vibrations due to the contact. The force feedback must take place at a very high frequency (often between $ 500 $ and $ 1\,000\,$Hz) for a smooth sense of touch. 
\end{description}
%
Although each of these steps alone is computationally demanding, the whole simulation process must be computed in real-time or close to real-time. Real-time means that one second of simulation corresponds to one second of real life. Of particular interest to us in this PhD is the accurate modelling of the deformation of anatomical structures in real-time.

### 2010-10-07 Thesis/Chapter10.tex
- Update 2 October -
A few changes in shell part + part of conclusion




git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@180 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
- Update 7 October -
Changes added in intro and conclusion + references improved + TODO removed



git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@183 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

Our idea is the following: while many flat triangles are required to describe highly curved surfaces, fewer triangular shell elements are needed to describe the given geometry with the same precision since they can be curved. Our goal is to create a mesh featuring the optimal number of shell elements while staying as close as possible to our targeted geometry. Literature about volumic mesh generation algorithms is fairly dense. However, there are only a few that are concerned about the generation of meshes over curved surfaces. One of the most widely used techniques for the creation of surface meshes is the plane to surface transformation method \citep{Zienkiewicz71}, mesh is first generated on a two-dimensional domain and then mapped onto the surface. If this method gives reasonably good meshes on smooth surfaces, the results are usually quite poor with more complex curved surfaces. The finite elements may be generated directly on the curved surfaces based on the advancing front technique \citep{Lo85,Lau96}. The main issue with this approach is that an analytical description of the geometry is needed, which is not the case in medical simulation. Another method consists of using an a priori error estimator to build an adaptive mesh generation \citep{Baumann97}. However, the tolerance of this indicator should be chosen depending on the desired accuracy of the finite element solution, and therefore requires some knowledge about the problem in order to choose an effective tolerance. \cite{Bechet02} start from an existing triangular mesh created with a CAD (computer-aided design) software and refine and smooth the mesh based on element quality and surface curvature. While all those methods allow their authors to get satisfactory meshes over curved surfaces according to their needs, they all make use of flat elements to mesh geometries and do not generate actual shells.

@@

In the following, we assume that we have a high resolution triangular mesh obtained from a binary segmented image of the object we want to simulate (via a Marching Cube algorithm for instance, \cite{Lorensen87}). We propose a technique that can simplify the high resolution mesh of the object to be simulated and approximate the surface of anatomical structures with shell elements whose each surface is described by the shape function used in our shell formulation. Thus, the first step in the process of generating a shell-based mesh is an important decimation of the high resolution mesh, using quadric edge collapse technique implemented in \cite{Meshlab}. MeshLab is an open source program for the processing and editing of unstructured 3D triangular meshes. The algorithm tries as much as possible to preserve mesh boundaries and generates high quality triangular elements. We then apply a heuristic method derived from the work of \cite{Saupin07} with tetrahedral meshes based on simple geometrical rules. For each node of the coarse mesh, we find the three closest triangles on the high resolution mesh and we move the node to the barycentre of the three centres of mass of those triangles. This technique locally smoothes the surface of the mesh while converging towards the desired high resolution mesh.

@@

\begin{figure}
\centering
\includegraphics[width=13.5cm]{chapter10/resultsAneurysm.pdf}
\caption {(a) the targeteted high resolution aneurysm mesh ($28\,368$ triangles). (b): the one-sided Hausdorff distance error map on a mesh of 772 shells generated with our method.}
\label{chap10:fig-aneurysm}
\end{figure}

\subsubsection*{Computation times.}
We perform several tests on the aneurysm model at different resolutions to measure computation times. The shells are resisting to a uniform pressure load and solved using a Conjugate Gradient (CG) iterative solver. The computation times are reported in \fig{chap10:fig-computation}. Implicit integration allows for large time steps ($40\,ms$) and the computation is real-time for 800 shell elements and a reasonable error criterion ($5\,\%$). When the computation time must be bounded (critical real-time applications), one can fix the number of CG iterations to, for instance, $100$ and remains real-time for $1\,000$ shell elements. However, in that case the accuracy of the results is not checked.
%
\begin{figure}
\centering
\includegraphics[width=13.5cm]{chapter10/computation_times.pdf}
\caption {Computation time on meshes of 200, 400, 600, 800 and $ 1\,000 $ elements.}.
\label{chap10:fig-computation}
\end{figure}

@@

An example of medical procedure to illustrate this point even further is angioplasty. Angioplasty is the technique of mechanically widening a narrowed or obstructed blood vessel, typically as a result of atherosclerosis. An empty and collapsed balloon on a guide wire is passed into the narrowed locations and then inflated to a fixed size. The balloon crushes the fatty deposits, so opening up the blood vessel to improved flow. As a proof of concept, we tried to simulate an angioplasty. Our preliminarty results are presented on \fig{chap10:fig-stent}. The blood vessel is modelled using the shell FEM formulation described in this paper and the fatty deposits are simulated with a tetrahedral FEM method and are fixed to the interior wall of the blood vessel. When the balloon inflates it crushes the deposits and they then apply a pressure onto the curved surfaces of shells modelling the interior wall. The forces are then distributed onto the mechanical nodes of the blood vessel mesh as detailed in section~\ref{chap9:interactions}, which widens the blood vessel as expected. 
%
\begin{figure}
\centering
\includegraphics[width=12cm]{chapter10/stenose_final.pdf}
\caption {Simulation of an angioplasty procedure. (a, c): A collapsed stent is inserted into the blood vessel simulated with our shell FEM formulation. The fatty deposits (in yellow) are modelled with tetrahedral FEM. (b, d): The stent is crushing the fatty deposits which creates a pressure onto the interior wall and widens the blood vessel.}
\label{chap10:fig-stent}
\end{figure}

>>>>

Our idea is the following: while many flat triangles are required to describe highly curved surfaces, fewer triangular shell elements are needed to describe a given geometry with the same precision since they can be curved. Our goal is to create a mesh featuring the optimal number of shell elements while staying as close as possible to our targeted geometry. Literature about volumic mesh generation algorithms is fairly dense. However, there are only a few that are concerned about the generation of meshes over curved surfaces. One of the most widely used techniques for the creation of surface meshes is the plane to surface transformation method \citep{Zienkiewicz71}, mesh is first generated on a two-dimensional domain and then mapped onto the surface. If this method gives reasonably good meshes on smooth surfaces, the results are usually quite poor with more complex curved surfaces. The finite elements may be generated directly on the curved surfaces based on the advancing front technique \citep{Lo85,Lau96}. The main issue with this approach is that an analytical description of the geometry is needed, which is not the case in medical simulation. Another method consists of using an a priori error estimator to build an adaptive mesh generation \citep{Baumann97}. However, the tolerance of this indicator should be chosen depending on the desired accuracy of the finite element solution, and therefore requires some knowledge about the problem in order to choose an effective tolerance. \cite{Bechet02} start from an existing triangular mesh created with a CAD (computer-aided design) software and refine and smooth the mesh based on element quality and surface curvature. While all those methods allow their authors to get satisfactory meshes over curved surfaces according to their needs, they all make use of flat elements to mesh geometries and do not generate actual shells.

@@

In the following, we assume that we have a high resolution triangular mesh obtained from a binary segmented image of the object we want to simulate (via a Marching Cube algorithm for instance, \cite{Lorensen87}). We propose a technique that can simplify the high resolution mesh of the object to be simulated and approximate the surface of anatomical structures with shell elements whose each surface is described by the shape function used in our shell formulation. Thus, the first step in the process of generating a shell-based mesh is an important decimation of the high resolution mesh, using quadric edge collapse technique implemented in \citeauthor{Meshlab}. MeshLab is an open source program for the processing and editing of unstructured 3D triangular meshes. The algorithm tries as much as possible to preserve mesh boundaries and generates high quality triangular elements. We then apply a heuristic method derived from the work of \cite{Saupin07} with tetrahedral meshes based on simple geometrical rules. For each node of the coarse mesh, we find the three closest triangles on the high resolution mesh and we move the node to the barycentre of the three centres of mass of those triangles. This technique locally smoothes the surface of the mesh while converging towards the desired high resolution mesh.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=13.5cm]{chapter10/resultsAneurysm.pdf}
\caption {(a) the targeteted high resolution aneurysm mesh ($28\,368$ triangles). (b): the one-sided Hausdorff distance error map on a mesh of 772 shells generated with our method.}
\label{chap10:fig-aneurysm}
\end{figure}

\subsubsection*{Computation times.}
We perform several tests on the aneurysm model at different resolutions to measure computation times. The shells are resisting to a uniform pressure load and solved using a Conjugate Gradient (CG) iterative solver. The computation times are reported in \fig{chap10:fig-computation}. Implicit integration allows for large time steps ($40\,ms$) and the computation is real-time for 800 shell elements and a reasonable error criterion ($5\,\%$). When the computation time must be bounded (critical real-time applications), one can fix the number of CG iterations to, for instance, $100$ and remains real-time for $1\,000$ shell elements. However, in that case the accuracy of the results is not checked.
%
\begin{figure}[ht]
\centering
\includegraphics[width=13.5cm]{chapter10/computation_times.pdf}
\caption {Computation time on meshes of 200, 400, 600, 800 and $ 1\,000 $ elements.}.
\label{chap10:fig-computation}
\end{figure}

@@

An example of medical procedure to illustrate this point even further is angioplasty. Angioplasty is the technique of mechanically widening a narrowed or obstructed blood vessel, typically as a result of atherosclerosis. An empty and collapsed balloon on a guide wire is passed into the narrowed locations and then inflated to a fixed size. The balloon crushes the fatty deposits, so opening up the blood vessel to improved flow. As a proof of concept, we tried to simulate an angioplasty. Our preliminarty results are presented on \fig{chap10:fig-stent}. The blood vessel is modelled using the shell FEM formulation described in this paper and the fatty deposits are simulated with a tetrahedral FEM method and are fixed to the interior wall of the blood vessel. When the balloon inflates it crushes the deposits and they then apply a pressure onto the curved surfaces of shells modelling the interior wall. The forces are then distributed onto the mechanical nodes of the blood vessel mesh as detailed in section~\ref{chap9:interactions}, which widens the blood vessel as expected. 
%
\begin{figure}[ht]
\centering
\includegraphics[width=12cm]{chapter10/stenose_final.pdf}
\caption {Simulation of an angioplasty procedure. (a, c): A collapsed stent is inserted into the blood vessel simulated with our shell FEM formulation. The fatty deposits (in yellow) are modelled with tetrahedral FEM. (b, d): The stent is crushing the fatty deposits which creates a pressure onto the interior wall and widens the blood vessel.}
\label{chap10:fig-stent}
\end{figure}
